\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Fisher S., Barry A., Abreu J., et al. A scalable, fully automated
  process for construction of sequence-ready human exome targeted
  capture libraries. Genome Biol 12, R1 (2011).
\item
  Karolchik, D., Hinrichs AS, Kent WJ., et al. The UCSC Table Browser
  data retrieval tool. Nucleic Acids Res 32, D493-496 (2004).
\item
  Gnirke A., Melnikov A., Maguire J., et al. Solution hybrid selection
  with ultra-long oligonucleotides for massively parallel targeted
  sequencing. Nat Biotechnol 27, 182- 189 (2009).
\item
  Li H. \& Durbin, R. Fast and accurate long-read alignment with
  Burrows-Wheeler transform. Bioinformatics 26, 589-595 (2010).
\item
  Li H., Handsaker B., Wysoker A., et al. The Sequence Alignment/Map
  format and SAMtools. Bioinformatics 25, 2078-2079 (2009).
\item
  DePristo MA., Banks E., Poplin R., et al. A framework for variation
  discovery and genotyping using next-generation DNA sequencing data.
  Nat Genet 43, 491-498 (2011).
\item
  Forbes SA, Bindal N., Bamford S., et al. COSMIC: mining complete
  cancer genomes in the Catalogue of Somatic Mutations in Cancer.
  Nucleic Acids Res 39, D945-950 (2011).
\item
  Compeau PE., Pevzner PA., Tesler, G. How to apply de Bruijn graphs to
  genome assembly. Nat Biotechnol 29, 987-991 (2011).
\item
  Okamura R, Boichard A, Kato S, Sicklick JK, Bazhenova L, Kurzrock R.
  Analysis of NTRK Alterations in Pan-Cancer Adult and Pediatric
  Malignancies: Implications for NTRK Targeted Therapeutics. JCO Precis
  Oncol. 2018;2018:10.1200/PO.18.00183.
\end{enumerate}
